results

### 2023-03-08 results_work.RMD
results_work updates

## Data
str.change <- readRDS("./data/data-gen/humac/str.change.RDS") # Untransfromed data
str.lchange <- readRDS("./data/data-gen/humac/str.lchange.RDS") # Log-transfromed data

## Linear mixed effects model

@@

## Emmeans
# Untransformed
str.emm <- confint(emmeans(str.mod, specs = ~"supplement|time")) %>%
  data.frame()

@@

# For inline plotting
strcoef <- coef(summary(str.mod))
pdiff.c4 <- round(strcoef[10,5], 2)

@@

At baseline, there were no significant differences between legs allocated to training with glucose or placebo in muscle mass, isometric or isokinetic peak torque (Tab 1). Total session volume (Tab 2) increased significantly from session 4 to session 6 compared to session 1 (*p* < 0.05), with no differences between exercising with glucose or placebo (*p* > 0.05). On pairwise consecutive days there were no significant differences in mean ingestion of protein, fat, carbohydrate or total calories (*p* > 0.05).

###### **Table 1:**  Baseline descriptives of legs allocated to RT with glucose or RT. LM = Lean mass, Strength = strength index, calculated from isometric and isokinetic peak torque, Iso 0 PT = Isometric (0 d/s) peak torque, Iso 60 PT = Isokinetic peak torque at 60 d/s, Iso 240 PT = Isokinetic peak torque at 240 d/s.
![](figures/tab1.png)
Glucose ingestion before and after RT led to significant increases in plasma levels of glucose (Fig 1B, 120min: 38 ± 4% [*p* = `r p.120`], 135min: 31 ± 4% [*p* = `r p.135`], 150min: 32 ± 4% [*p* = `r p.150`]) and c-peptide (Fig 1C, 120min: 95 ± 10% [*p* = `r cpp.120`], 150min: 87 ± 10% [*p* = `r cpp.150`]) before, during and after the session, compared to no change in placebo (*p* > 0.05). At 2hrs post-exercise, RT with glucose led to significantly lower plasma glucose levels compared to RT with placebo (1B, 270min: -8 ± 4% [*p* = `r p.270`].

@@

After 5 RT sessions (Fig 1D, Post 5RT), there was a significant difference in strength between glucose and placebo,  where placebo decreased strength 7% more than glucose (Fig 1D, *p* = `r pdiff.c4`). At the remaining time points, there were no significant differences between exercising with glucose and placebo (*p* > 0.05). While both RT with glucose and placebo led to significantly reduced strength post fifth session compared to baseline (*p* < 0.05), there were no significant differences in strength at baseline and 23hrs post sixth RT session (Fig 1D, Baseline and 23h post 6RT).

>>>>

## Data
# Full data - baseline -> 23h post 6RT
str.change <- readRDS("./data/data-gen/humac/str.change.RDS") # Untransfromed data
str.lchange <- readRDS("./data/data-gen/humac/str.lchange.RDS") # Log-transfromed data

# Acute data - Post 5RT -> 23h post 6RT
astr.change <- readRDS("./data/data-gen/humac/astr.change.RDS") # Untransfromed data
astr.lchange <- readRDS("./data/data-gen/humac/astr.lchange.RDS") # Log-transfromed data

## Linear mixed effects model full data

@@

## Emmeans full data
# Untransformed
str.emm <- confint(emmeans(str.mod, specs = ~"supplement|time")) %>%
  data.frame()

@@

## Linear mixed effects model acute
# Untransformed
astr.mod <- lmerTest::lmer(change ~ 0 + baseline + time + supplement:time + (1|subject),
                        data = astr.change)

astr.res <- plot(astr.mod)
astr.sum <- summary(astr.mod)

# Log-transformed
astr.lmod <- lmerTest::lmer(change ~ 0 + baseline + time + supplement:time + (1|subject),
                         data = astr.lchange)

astr.lres <- plot(astr.lmod)
astr.lsum <- summary(astr.lmod)

## Emmeans acute data
astr.emm <- confint(emmeans(astr.mod, specs = ~"supplement|time")) %>%
  data.frame()

astr.lmod <- confint(emmeans(astr.lmod, specs = ~"supplement|time")) %>%
  data.frame()

## For inline plotting full data
strcoef <- coef(summary(str.mod))

# Time points compared to baseline (full data)
pc2 <- round(strcoef[2,5], 3)
pc3 <- round(strcoef[3,5], 3)
pscient.c4 <- round(strcoef[4,5], 40)
pc4 <- sprintf("%.5f", 7.886277e-06)
pc5 <- round(strcoef[5,5], 3)
pc6 <- round(strcoef[6,5], 3)
pc7 <- round(strcoef[7,5], 5)

# Glucose compared to placebo (full data)
pdiff.c2 <- round(strcoef[8,5], 3)
pdiff.c3 <- round(strcoef[9,5], 3)
pdiff.c4 <- round(strcoef[10,5], 3)
pdiff.c5 <- round(strcoef[11,5], 3)
pdiff.c6 <- round(strcoef[12,5], 3)
pdiff.c7 <- round(strcoef[13,5], 3)

## For inline plotting acute data
astrcoef <- coef(summary(astr.mod))
apc2 <- round(astrcoef[2,5], 3)
apc3 <- round(astrcoef[3,5], 3)
apc4 <- round(astrcoef[4,5], 3)

@@

```{r volume model}
## Scripts
# - volume.cleanup.R
# - volume.analysis.R

## Data
vol.change <- readRDS("./data/data-gen/training/vol.change.RDS") # Untransformed data
vol.lchange <- readRDS("./data/data-gen/training/vol.lchange.RDS") # Log-transformed data

## Models

# Untransformed 
vol.mod <- lmerTest::lmer(change ~ 0 + baseline + time + supplement:time + (1|subject),
                     data = vol.change)
vol.res <- plot(vol.mod)
vol.sum <- summary(vol.mod)

# Log-transformed
vol.lmod <- lmerTest::lmer(change ~ 0 + baseline + time + supplement:time + (1|subject),
                     data = vol.lchange)

vol.lres <- plot(vol.lmod)
vol.lsum <- summary(vol.lmod)

# Untransformed
vol.emm <- confint(emmeans(vol.mod, specs = ~"supplement|time")) %>%
  data.frame()

# Log-transformed
vol.lemm <- confint(emmeans(vol.lmod, specs = ~"supplement|time")) %>%
  data.frame()

## For inline plotting

# Sessions compared to baseline
volcoef <- coef(summary(vol.mod))
pvol.s2 <- round(volcoef[2,5], 4)
pvol.s3 <- round(volcoef[3,5], 4)
pvol.s4 <- round(volcoef[4,5], 4)
pvol.s5 <- round(volcoef[5,5], 3)
pvol.s6 <- round(volcoef[6,5], 5)

# Glucose compared to plac
pvol.c2 <- round(volcoef[7,5], 3) 
pvol.c3 <- round(volcoef[8,5], 3) 
pvol.c4 <- round(volcoef[9,5], 3) 
pvol.c5 <- round(volcoef[10,5], 3) 
pvol.c6 <- round(volcoef[11,5], 3)

There were no difference in mean change of total training session volume between exercising with placebo or glucose, with an increase of 18 and 16% from session 1 to session 6, respectively (Tab 2; Mean change, 2: *p* = `r pvol.c2`, 3: *p* = `r pvol.c3`, 4: *p* = `r pvol.c4`, 5: *p* = `r pvol.c5`, 6: *p* = `r pvol.c6`). Both exercising with glucose and placebo led to significant increases in mean total training session volume at session four, five and six, compared to session 1 (Tab 2; Mean change, 2: *p* = `r pvol.s2`, 3: *p* = `r pvol.s3`, 4: *p* = `r pvol.s4`, 5: *p* = `r pvol.s5`, 6: *p* = `r pvol.s6`). In regard to the dietary intervention, there were no difference in mean macro nutrient intake (protein, fat, carbohydrates) or total calorie intake between glucose and placebo on pairwise consecutive days (*p* > 0.05).

@@

Glucose ingestion before and after RT led to significant increases in plasma levels of glucose by 38% immediately before RT (Fig 1B, 0 min: *p* = `r p.120`), by 31% during RT (1B, 15 min: *p* = `r p.135`) and by 32% immediately after RT (1B, 30 min: *p* = `r p.150`), compared to placebo ingestion before and after RT. Two hours after the session, RT with glucose measured 8% lower plasma glucose levels compared to RT with placebo (1B, 270min: *p* = `r p.270`). Similarly, levels of c-peptide increased significantly more in exercises with glucose compared to placebo, by 95% immediately before (Fig 1C, 0 min: *p* = `r cpp.120`) and 87% after RT (1C, 30 min: *p* = `r cpp.150`).

After 5 RT sessions (Fig 1D, Post 5RT), there was a significant difference in strength between glucose and placebo,  where placebo decreased strength 7% more than glucose (1D, *p* = `r pdiff.c4`). At the remaining time points, there were no significant differences in mean change between exercising with glucose and placebo (1D, Post 2RT: *p* = `r pdiff.c2`, Post 4RT: *p* = `r pdiff.c3`, 30min post 6RT: *p* = `r pdiff.c5`, 2h post 6RT: *p* = `r pdiff.c6`, 23h post 6RT: *p* = `r pdiff.c7`). Both RT with glucose and placebo led to significantly reduced strength post fifth session compared to baseline, by 11 and 18% respectively (1D, Post 5RT: *p* = `r pc4`). Comparisons of the acute data gathered from post fifth session until and including 23hrs post sixth session showed a significant mean increase in strength of 5-9% after RT with glucose and placebo 30min after sixth RT session (1D, 30min post 6RT: *p* = `r apc2`) and two hours after sixth RT session (1D, 2h post 6RT: *p* = `r apc3`). Twenty-three hours after the last RT, strength was unchanged compared to after fifth RT session (23h post 6RT: *p* = `r apc4`).
